Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2016-12-30 Papers/2017/LogicaUniversalis-HajekAndersonControversy/main.tex
modifications requested by report 1

\usepackage{amsmath}
\usepackage{xspace}
\usepackage{url}
\usepackage{commands}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{modallogics}
\usepackage[backend=biber,sorting=ydnt,maxnames=999,maxcitenames=999,maxbibnames=999,natbib]{biblatex}
\addbibresource[label=bibs]{Bibliography.bib}

@@

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[A1] Either a property or its negation is positive, but not
  both:
  $$\hol{\allq \varphi [P(\neg \varphi) \biimp \neg P(\varphi)]}$$
\item[A2] A property necessarily implied by a
  positive property is positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp P(\psi)]}$$
\item[T1] Positive properties are possibly exemplified:
  $$\hol{\allq \varphi [P(\varphi) \imp \pos \exq x \varphi(x)]}$$
\item[D1] A \emph{God-like} being possesses all positive properties:
  $$\hol{G(x) \equiv \forall \varphi [P(\varphi) \imp \varphi(x)]}$$
\item[A3]  The property of being God-like is positive:
  $$\hol{P(G)}$$
\item[C\phantom{1}] Possibly, a God-like being exists: $$\hol{\pos \exq x G(x)}$$
\item[A4]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$
\item[D2] An \emph{essence} of an individual is a property possessed by it and necessarily implying any of its properties: $$\hol{\ess{\varphi}{x} \equiv \varphi(x) \wedge \allq
  \psi (\psi(x) \imp \nec \allq y (\varphi(y) \imp \psi(y)))}$$
\item[T2]  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G(x) \imp \ess{G}{x}]}$$
\item[D3] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE(x) \equiv \allq \varphi [\ess{\varphi}{x} \imp \nec
  \exq y \varphi(y)]}$$
\item[A5] Necessary existence is a positive property: $$\hol{P(\NE)}$$
\item[L1] If a god-like being exists, then necessarily a god-like being exists:
  $$\hol{\exq x G(x) \imp \nec \exq y G(y)}$$
\item[L2] If possibly a god-like being exists, then necessarily a god-like being exists:
  $$\hol{\pos \exq x G(x) \imp \nec \exq y G(y)} $$
%
\item[T3] Necessarily, a God-like being exists: $$\hol{\nec \exq x G(x)}$$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Scott's version of G\"odel's ontological argument\label{fig:Goedel}}
\end{figure}

@@

For both \textbf{constant domain semantics} and \textbf{varying domain
semantics}, the following results hold for \emph{Anderson's
Emendation} (cf. Fig. \ref{fig:Anderson}): T1, C
and T3' can be quickly automated (in logics \K, \K and \KB,
respectively); the axioms A4 and A5' are proven redundant (the former in logic \KFourB and the latter
already in \K); a trivial countermodel (with two worlds and  two
individuals) for MC is generated by Nitpick (for all mentioned
logics); all axioms and definitions are shown to be mutually
consistent.

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[A:A1] If a property is positive, its negation is not positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \neg P(\neg \varphi)]}$$
\item[A2] A property necessarily implied by a
  positive property is positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp P(\psi)]}$$
\item[T1] Positive properties are possibly exemplified:
  $$\hol{\allq \varphi [P(\varphi) \imp \pos \exq x \varphi(x)]}$$
\item[A:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive:
  $$\hol{G_A(x) \equiv \forall \varphi [P(\varphi) \biimp \nec \varphi(x)]}$$
\item[A3']  The property of being God-like is positive:
  $$\hol{P(G_A)}$$
\item[C\phantom{1}] Possibly, a God-like being exists: $$\hol{\pos \exq x G(x)}$$
\item[A4]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$
\item[T2']  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G_A(x) \imp \essA{G_A}{x}]}$$
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y \varphi(y)]}$$
\item[A5'] Necessary existence is a positive property: $$\hol{P(\NE_A)}$$
\item[L1'] If a god-like being exists, then necessarily a god-like being exists:
  $$\hol{\exq x G_A(x) \imp \nec \exq y G_A(y)}$$
\item[L2'] If possibly a god-like being exists, then necessarily a god-like being exists:
  $$\hol{\pos \exq x G_A(x) \imp \nec \exq y G_A(y)} $$
%
\item[T3'] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_A(x)}$$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Anderson's Emendation \label{fig:Anderson}}
\end{figure}

The redundancy of A4 and A5 is particularly controversial. Magari
\cite{Magari1988} claimed that A4 and A5 are superfluous, arguing that T3 is true in all
models of the other axioms and definitions by Gödel.
\citet[p.~5-6]{Hajek_Magari_and_others_1996} investigated this
further, and claimed that Magari's claim is not valid, but is
nevertheless true  under additional silent assumptions by Magari.
Moreover, \citet[p.~2]{Hajek_Magari_and_others_1996} cites his earlier
work\footnote{Although \citep{Hajek_der_Mathematiker_2001} precedes
\citep{Hajek_Magari_and_others_1996} in writing, it was published only
5 years later, in German.} \citep{Hajek_der_Mathematiker_2001}, where
he claims (in Theorem 5.3) that for Anderson's emended theory
\citep{anderson90:_some_emend_of_goedel_ontol_proof}, A4 and A5 are
not only superfluous, but also redundant. \citet[footnote 1 in
p.~1]{AndersonGettings}, in a footnote, rebutted Hájek's claim,
arguing that the redundancy of A4 and A5 holds only under constant
domain semantics, while Anderson's emended theory ought to be taken
under Cocchiarella's semantics \citep{Cocchiarella} (a varying domain
semantics). Our results show that Hájek was originally right, under
both constant and varying domain semantics.

Nevertheless, \citet[p.~7]{Hajek2002} acknowledges Anderson's rebuttal,
and apparently accepts it, as evidenced by his use\footnote{
  A4 and A5 are used by \citet[p.~11]{Hajek2002} in,
  respectively, Lemma 4 and Theorem 4.
}
of A4 and A5', as well as varying domain semantics, in his new
emendation (named \AOEH\/ \citep[sec.~4]{Hajek2002}, cf. Fig.
\ref{fig:Hajek1}), which replaces Anderson's A:A1 and A2 by a simpler
axiom H:A12. Surprisingly, the computer-assisted formalization of
\AOEH\ shows that A4 and A5' are still superfluous. Moreover,
A4 and A5' are independent
of the other axioms and definitions.
Therefore, A4 and A5' are not redundant, despite their superfluousness.

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are necessarily implied by a positive property:
  $$\hol{G_H(x) \equiv \forall \varphi [\nec \varphi(x) \biimp \exq \psi[P(\psi) \wedge \nec \allq x [\psi(x)  \imp \varphi(x))]]}$$
\item[A3']  The property of being God-like is positive:
  $$\hol{P(G_H)}$$
\item[A4]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[A5'] Necessary existence is a positive property: $$\hol{P(\NE_A)}$$

\item[L3]
  \begin{itemize}
  \item[(1)] The negation of a positive property is not positive:
$$\hol{\allq \varphi[P(\varphi) \imp \neg P(\neg \varphi)] }$$
  \item[(2)] Positive properties are possibly exemplified:
$$\hol{\allq \varphi[P(\varphi) \imp \pos \exq x \varphi(x)] }$$
  \item[(3)] If a god-like being exists, then necessarily a god-like being exists:
$$\hol{\allq x[G_H(x) \imp \nec G_H(x)))] }$$
  \item[(4)] All positive properties are necessarily implied by the property of being god-like:
$$\hol{\allq \varphi[P(\varphi) \imp \nec \allq x[G_H(x) \imp \varphi(x)]] }$$
  \end{itemize}
\item[L4]  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G_H(x) \imp \ess{G_H}{x}]}$$

\item[T3'] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_H(x)}$$
%
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Hájek's First Emendation \AOEH} \label{fig:Hajek1}
\end{figure}

Although Hájek did not notice the superfluousness of A4 and A5' in his
\AOEH, he did describe yet another emendation (his \AOEHH, cf.
Fig. \ref{fig:Hajek2}) where A4 and A5' are superfluous (though no
claim is made w.r.t. to their redundancy), if A3' is replaced by a
stronger axiom (H:A3) additionally stating that the property of actual
existence is positive when it comes to God-like beings
\cite[sec.~5]{Hajek2002}. Formalization of \AOEHH\ shows that A4 is
not only superflous, but also redundant. In addition, A5' becomes superfluous
and independent. Surprisingly, a countermodel for the weaker
A3' was succesfully generated. This is somewhat unsatisfactory (for
theistic goals), because it shows that \AOEHH\ does not entail the
positiveness of being God-like.

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[A:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive:
  $$\hol{G_A(x) \equiv \forall \varphi [P(\varphi) \biimp \nec \varphi(x)]}$$
\item[H:A3]  The property of being God-like and existing actually is positive:
  $$\hol{P(G_A \wedge E)}$$
\item[T3'] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_A(x)}$$
%
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Hájek's Second Emendation \AOEHH \label{fig:Hajek2}}
\end{figure}

Nevertheless, \AOEHH\ is explicitly regarded by
\citet[p.~12]{Hajek2002} as just an intermediary step towards a more
natural theory, based on a more sophisticated notion of positiveness.
That is his final emendation (\AOEHHH, cf. Fig. \ref{fig:Hajek3}), which
restores A3' and does use A4 and A5', albeit in a modified form (i.e.
H:A4 and H:A5).

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[D4]  A property is positive\textsuperscript{\#} iff it is necessarily implied by a positive property:
  $$\hol{P^\#(\varphi) \equiv \exq \psi[P(\psi) \wedge \nec \allq x[\psi(x) \imp \varphi(x)]]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive\textsuperscript{\#}:
  $$\hol{G_H(x) \equiv \forall \varphi [P^\#(\varphi) \biimp \nec \varphi(x)]}$$
\item[A3']  The property of being God-like is positive:
  $$\hol{P(G_H)}$$
\item[H:A4]  Positive\textsuperscript{\#} properties are necessarily positive\textsuperscript{\#}:
  $$\hol{\allq \varphi [P^\#(\varphi) \imp \Box \; P^\#(\varphi)]}$$
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[H:A5] Necessary existence is a positive\textsuperscript{\#} property: $$\hol{P^\#(\NE_A)}$$
%
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Hájek's Third Emendation \AOEHHH \label{fig:Hajek3}}
\end{figure}

The formalization of \AOEHHH\ shows that both H:A4 and H:A5 are superfluous
aswell as independent. For the old A5', no conclusive results were achieved.

Additionally, Anderson \citep[footnote
14]{anderson90:_some_emend_of_goedel_ontol_proof} (cf. Fig. \ref{fig:Anderson_simp}) remarks that only
the quantifiers in T3' and in A:D2 need to be interpreted as
actualistic quantifiers, while others may be taken as possibilistic
quantifiers. Our computer-assisted study of this mixed variant shows
that A4 is still redundant in logic \KFourB, but A5' becomes independent (hence not
redundant). Unfortunately, a countermodel for T3 can then be found.

@@

\begin{itemize}
\item[AS:D1] A property is positive iff its absence necessarily renders an individual defective and it is possible
  that an individual has the property without being defective.
   $$\hol{P_{AS}(\varphi) \equiv \nec (\allq x (\neg \varphi(x) \imp D(x)) \wedge (\neg \nec \allq x (\varphi(x) \imp D(x))))}$$
\item[A:A1'] If a property is positive, its negation is not positive:
  $$\hol{\allq \varphi [P_{AS}(\varphi) \imp \neg P_{AS}(\neg \varphi)]}$$
\item[A2'] A property necessarily implied by a
  positive property is positive:
  $$\hol{\allq \varphi \allq \psi [(P_{AS}(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp P_{AS}(\psi)]}$$
\item[A4']  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P_{AS}(\varphi) \imp \nec P_{AS}(\varphi)]}$$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Anderson's Simplification \label{fig:Anderson_simp}}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{xspace}
\usepackage{url}
\usepackage{rotating}
\usepackage{commands}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{modallogics}
\usepackage{xcolor}
\usepackage[backend=biber,sorting=ydnt,maxnames=999,maxcitenames=999,maxbibnames=999,natbib]{biblatex}
\addbibresource[label=bibs]{Bibliography.bib}

@@

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[A1] Either a property or its negation is positive, but not
  both:
  $$\hol{\allq \varphi [P(\neg \varphi) \biimp \neg P(\varphi)]}$$
\item[A2] A property necessarily implied by a
  positive property is positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp P(\psi)]}$$
\item[T1] Positive properties are possibly exemplified:
  $$\hol{\allq \varphi [P(\varphi) \imp \pos \exq x \varphi(x)]}$$
\item[D1] A \emph{God-like} being possesses all positive properties:
  $$\hol{G(x) \equiv \forall \varphi [P(\varphi) \imp \varphi(x)]}$$
\item[A3]  The property of being God-like is positive:
  $$\hol{P(G)}$$
\item[C\phantom{1}] Possibly, a God-like being exists: $$\hol{\pos \exq x G(x)}$$
\item[A4]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$
\item[D2] An \emph{essence} of an individual is a property possessed by it and necessarily implying any of its properties: $$\hol{\ess{\varphi}{x} \equiv \varphi(x) \wedge \allq
  \psi (\psi(x) \imp \nec \allq y (\varphi(y) \imp \psi(y)))}$$
\item[T2]  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G(x) \imp \ess{G}{x}]}$$
\item[D3] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE(x) \equiv \allq \varphi [\ess{\varphi}{x} \imp \nec
  \exq y \varphi(y)]}$$
\item[A5] Necessary existence is a positive property: $$\hol{P(\NE)}$$
\item[L1] If a God-like being exists, then necessarily a God-like being exists:
  $$\hol{\exq x G(x) \imp \nec \exq y G(y)}$$
\item[L2] If possibly a God-like being exists, then necessarily a God-like being exists:
  $$\hol{\pos \exq x G(x) \imp \nec \exq y G(y)} $$
%
\item[T3] Necessarily, a God-like being exists: $$\hol{\nec \exq x G(x)}$$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Scott's version of G\"odel's ontological argument\label{fig:Goedel}}
\end{figure}

@@

For both \textbf{constant domain semantics} and \textbf{varying domain
semantics}, the following results hold for \emph{Anderson's
Emendation} (cf. Fig. \ref{fig:Anderson}): T1, C
and T3$'$ can be quickly automated (in logics \K, \K and \KB,
respectively); the axioms A4 and A5$'$ are proven redundant (the former in logic \KFourB and the latter
already in \K); a trivial countermodel (with two worlds and  two
individuals) for MC is generated by Nitpick (for all mentioned
logics); all axioms and definitions are shown to be mutually
consistent.

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[A:A1] If a property is positive, its negation is not positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \neg P(\neg \varphi)]}$$
\item[A2] A property necessarily implied by a
  positive property is positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp P(\psi)]}$$
\item[T1] Positive properties are possibly exemplified:
  $$\hol{\allq \varphi [P(\varphi) \imp \pos \exq x \varphi(x)]}$$
\item[A:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive:
  $$\hol{G_A(x) \equiv \forall \varphi [P(\varphi) \biimp \nec \varphi(x)]}$$
\item[A3$'$]  The property of being God-like is positive:
  $$\hol{P(G_A)}$$
\item[C\phantom{1}] Possibly, a God-like being exists: $$\hol{\pos \exq x G(x)}$$
\item[A4]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$
\item[T2$'$]  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G_A(x) \imp \essA{G_A}{x}]}$$
\item[D3$'$] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y \varphi(y)]}$$
\item[A5$'$] Necessary existence is a positive property: $$\hol{P(\NE_A)}$$
\item[L1$'$] If a God-like being exists, then necessarily a God-like being exists:
  $$\hol{\exq x G_A(x) \imp \nec \exq y G_A(y)}$$
\item[L2$'$] If possibly a God-like being exists, then necessarily a God-like being exists:
  $$\hol{\pos \exq x G_A(x) \imp \nec \exq y G_A(y)} $$
%
\item[T3$'$] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_A(x)}$$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Anderson's Emendation \label{fig:Anderson}}
\end{figure}

The redundancy of A4 and A5 is particularly controversial. Magari
\cite{Magari1988} claimed that A4 and A5 are superfluous, arguing that T3 is true in all
models of the other axioms and definitions by Gödel.
\citet[pp.~5--6]{Hajek_Magari_and_others_1996} investigated this
further, and claimed that Magari's claim is not valid, but is
nevertheless true  under additional silent assumptions by Magari.
Moreover, \citet[p.~2]{Hajek_Magari_and_others_1996} cites his earlier
work\footnote{Although \citep{Hajek_der_Mathematiker_2001} precedes
\citep{Hajek_Magari_and_others_1996} in writing, it was published only
5 years later, in German.} \citep{Hajek_der_Mathematiker_2001}, where
he claims (in Theorem 5.3) that for Anderson's emended theory
\citep{anderson90:_some_emend_of_goedel_ontol_proof}, A4 and A5 are
not only superfluous, but also redundant. \citet[footnote 1 in
p.~1]{AndersonGettings}, in a footnote, rebutted Hájek's claim,
arguing that the redundancy of A4 and A5 holds only under constant
domain semantics, while Anderson's emended theory ought to be taken
under Cocchiarella's semantics \citep{Cocchiarella} (a varying domain
semantics). Our results show that Hájek was originally right, under
both constant and varying domain semantics.

Nevertheless, \citet[p.~7]{Hajek2002} acknowledges Anderson's rebuttal,
and apparently accepts it, as evidenced by his use\footnote{
  A4 and A5 are used by \citet[p.~11]{Hajek2002} in,
  respectively, Lemma 4 and Theorem 4.
}
of A4 and A5$'$, as well as varying domain semantics, in his new
emendation (named \AOEH\/ \citep[sec.~4]{Hajek2002}, cf. Fig.
\ref{fig:Hajek1}), which replaces Anderson's A:A1 and A2 by a simpler
axiom H:A12. Surprisingly, the computer-assisted formalization of
\AOEH\ shows that A4 and A5$'$ are still superfluous. Moreover,
A4 and A5$'$ are independent
of the other axioms and definitions.
Therefore, A4 and A5$'$ are not redundant, despite their superfluousness.

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are necessarily implied by a positive property:
  $$\hol{G_H(x) \equiv \forall \varphi [\nec \varphi(x) \biimp \exq \psi[P(\psi) \wedge \nec \allq x [\psi(x)  \imp \varphi(x))]]}$$
\item[A3$'$]  The property of being God-like is positive:
  $$\hol{P(G_H)}$$
\item[A4]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P(\varphi) \imp \Box \; P(\varphi)]}$$
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$
\item[D3$'$] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[A5$'$] Necessary existence is a positive property: $$\hol{P(\NE_A)}$$

\item[L3]
  \begin{itemize}
  \item[(1)] The negation of a positive property is not positive:
$$\hol{\allq \varphi[P(\varphi) \imp \neg P(\neg \varphi)] }$$
  \item[(2)] Positive properties are possibly exemplified:
$$\hol{\allq \varphi[P(\varphi) \imp \pos \exq x \varphi(x)] }$$
  \item[(3)] If a God-like being exists, then necessarily a God-like being exists:
$$\hol{\allq x[G_H(x) \imp \nec G_H(x)))] }$$
  \item[(4)] All positive properties are necessarily implied by the property of being God-like:
$$\hol{\allq \varphi[P(\varphi) \imp \nec \allq x[G_H(x) \imp \varphi(x)]] }$$
  \end{itemize}
\item[L4]  Being God-like is an essence of any
  God-like being: $$\hol{\allq x [G_H(x) \imp \ess{G_H}{x}]}$$

\item[T3$'$] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_H(x)}$$
%
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Hájek's First Emendation \AOEH} \label{fig:Hajek1}
\end{figure}

Although Hájek did not notice the superfluousness of A4 and A5$'$ in his
\AOEH, he did describe yet another emendation (his \AOEHH, cf.
Fig. \ref{fig:Hajek2}) where A4 and A5$'$ are superfluous (though no
claim is made w.r.t. to their redundancy), if A3$'$ is replaced by a
stronger axiom (H:A3) additionally stating that the property of actual
existence is positive when it comes to God-like beings
\cite[sec.~5]{Hajek2002}. Formalization of \AOEHH\ shows that A4 is
not only superflous, but also redundant. In addition, A5$'$ becomes superfluous
and independent. Surprisingly, a countermodel for the weaker
A3$'$ was succesfully generated. This is somewhat unsatisfactory (for
theistic goals), because it shows that \AOEHH\ does not entail the
positiveness of being God-like.

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[A:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive:
  $$\hol{G_A(x) \equiv \forall \varphi [P(\varphi) \biimp \nec \varphi(x)]}$$
\item[H:A3]  The property of being God-like and existing actually is positive:
  $$\hol{P(G_A \wedge E)}$$
\item[T3$'$] Necessarily, a God-like being exists: $$\hol{\nec \exq x G_A(x)}$$
%
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Hájek's Second Emendation \AOEHH \label{fig:Hajek2}}
\end{figure}

Nevertheless, \AOEHH\ is explicitly regarded by
\citet[p.~12]{Hajek2002} as just an intermediary step towards a more
natural theory, based on a more sophisticated notion of positiveness.
That is his final emendation (\AOEHHH, cf. Fig. \ref{fig:Hajek3}), which
restores A3$'$ and does use A4 and A5$'$, albeit in a modified form (i.e.
H:A4 and H:A5).

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[D4]  A property is positive\textsuperscript{\#} iff it is necessarily implied by a positive property:
  $$\hol{P^\#(\varphi) \equiv \exq \psi[P(\psi) \wedge \nec \allq x[\psi(x) \imp \varphi(x)]]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive\textsuperscript{\#}:
  $$\hol{G_H(x) \equiv \forall \varphi [P^\#(\varphi) \biimp \nec \varphi(x)]}$$
\item[A3$'$]  The property of being God-like is positive:
  $$\hol{P(G_H)}$$
\item[H:A4]  Positive\textsuperscript{\#} properties are necessarily positive\textsuperscript{\#}:
  $$\hol{\allq \varphi [P^\#(\varphi) \imp \Box \; P^\#(\varphi)]}$$
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$
\item[D3$'$] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[H:A5] Necessary existence is a positive\textsuperscript{\#} property: $$\hol{P^\#(\NE_A)}$$
%
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Hájek's Third Emendation \AOEHHH \label{fig:Hajek3}}
\end{figure}

The formalization of \AOEHHH\ shows that both H:A4 and H:A5 are superfluous
as well as independent. For the old A5$'$, no conclusive results were achieved.

Additionally, Anderson \citep[footnote
14]{anderson90:_some_emend_of_goedel_ontol_proof} (cf. Fig. \ref{fig:Anderson_simp}) remarks that only
the quantifiers in T3$'$ and in A:D2 need to be interpreted as
actualistic quantifiers, while others may be taken as possibilistic
quantifiers. Our computer-assisted study of this mixed variant shows
that A4 is still redundant in logic \KFourB, but A5$'$ becomes independent (hence not
redundant). Unfortunately, a countermodel for T3 can then be found.

@@

\begin{itemize}
\item[AS:D1] A property is positive iff its absence necessarily renders an individual defective and it is possible
  that an individual has the property without being defective.
   $$\hol{P_{AS}(\varphi) \equiv \nec (\allq x (\neg \varphi(x) \imp D(x)) \wedge (\neg \nec \allq x (\varphi(x) \imp D(x))))}$$
\item[A:A1$'$] If a property is positive, its negation is not positive:
  $$\hol{\allq \varphi [P_{AS}(\varphi) \imp \neg P_{AS}(\neg \varphi)]}$$
\item[A2$'$] A property necessarily implied by a
  positive property is positive:
  $$\hol{\allq \varphi \allq \psi [(P_{AS}(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp P_{AS}(\psi)]}$$
\item[A4$'$]  Positive properties are necessarily positive:
  $$\hol{\allq \varphi [P_{AS}(\varphi) \imp \nec P_{AS}(\varphi)]}$$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Anderson's Simplification \label{fig:Anderson_simp}}
\end{figure}
